The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
add boertje 1985

## Caribou socioecology
Caribou are gregarious ungulates with fission-fusion dynamics [@Lesmerises_2018]
that display temporal and spatial variation in social networks [@Peignier_2019].
Caribou dig holes, termed craters, in winter to access forage beneath the snow
[@Bergerud_1974]. Cratering is presumed to be a costly behaviour, and as a
result, caribou tend to occupy and re-use craters once they are established.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. Access to forage is therefore heterogeneous in winter and depends
on snow cover and distribution of craters on the landscape. Home range sizes for 
caribou on Fogo Island are on average 50.1 $km^2$ in winter and 17.5 $km^2$ in 
summer [@Peignier_2019].

>>>>

## Caribou socioecology
Caribou are gregarious ungulates with fission-fusion dynamics [@Lesmerises_2018]
that display temporal and spatial variation in social networks [@Peignier_2019].
Caribou dig holes, termed craters, in winter to access forage beneath the snow
[@Bergerud_1974]. Cratering is presumed to be a costly behaviour [@Boertje_1985], and as a
result, caribou tend to occupy and re-use craters once they are established.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. Access to forage is therefore heterogeneous in winter and depends
on snow cover and distribution of craters on the landscape.
